MSDS6372Project1

### 2021-01-22 MSDS6372Project1.Rmd
some more
forgot to update rmd

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# Fixing three empty values in CarData$Engine.Fuel.Type, after research they are regular unleaded
CarData$Engine.Fuel.Type = ifelse(CarData$Engine.Fuel.Type=="","regular unleaded",CarData$Engine.Fuel.Type)
# Fixing Engine Cylinders to 0 -- Mazda RX or Electrical Vehicle
CarData$Engine.Cylinders = ifelse(is.na(CarData$Engine.Cylinders),0,CarData$Engine.Cylinders)
# Fixing Tesla Model S with Number.of.Doors missing
CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Tesla HP with mean HP found online of 510
#CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Ferrari FF 2013 Number.of.Doors to 2 -- Google research
CarData$Number.of.Doors = ifelse(CarData$Make=="Ferrari"&is.na(CarData$Number.of.Doors),2,CarData$Number.of.Doors)

@@

CarData %>% select(Market.Category,Performance,'High-Performance','Flex Fuel')

@@

# Look at summary of data
summary(CarData)

missingData = CarData[rowSums(is.na(CarData)) > 0,]
missingData
dim(missingData)

#Looking at Tesla
#CarData %>% filter(Make=="Tesla")

# Looking at what to do with Market.Category variable
marketCat = CarData %>% select(MSRP,Market.Category)
dim(marketCat)
head(marketCat,100)

>>>>

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# Fixing three empty values in CarData$Engine.Fuel.Type, after research they are regular unleaded
CarData$Engine.Fuel.Type = ifelse(CarData$Engine.Fuel.Type=="","regular unleaded",CarData$Engine.Fuel.Type)
# Fixing Engine Cylinders to 0 -- Mazda RX or Electrical Vehicle
CarData$Engine.Cylinders = ifelse(is.na(CarData$Engine.Cylinders),0,CarData$Engine.Cylinders)
# Fixing Tesla Model S with Number.of.Doors missing
CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Tesla HP with mean HP found online of 510
#CarData$Number.of.Doors = ifelse(CarData$Make=="Tesla"&is.na(CarData$Number.of.Doors),4,CarData$Number.of.Doors)
# Fixing Ferrari FF 2013 Number.of.Doors to 2 -- Google research
CarData$Number.of.Doors = ifelse(CarData$Make=="Ferrari"&is.na(CarData$Number.of.Doors),2,CarData$Number.of.Doors)
# Fixing FIAT 500e HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="FIAT"&is.na(CarData$Engine.HP),111,CarData$Engine.HP)
# Fixing Lincoln Continental HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Lincoln"&is.na(CarData$Engine.HP),345,CarData$Engine.HP)
# Fixing Ford Escape HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Ford"&is.na(CarData$Engine.HP),210,CarData$Engine.HP)
# Fixing Honda Fit EV HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Honda"&is.na(CarData$Engine.HP),123,CarData$Engine.HP)
# Fixing Mitsubishi i-MiEV HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Mitsubishi"&is.na(CarData$Engine.HP),66,CarData$Engine.HP)
# Fixing Chevrolet  Impala HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Chevrolet"&is.na(CarData$Engine.HP),305,CarData$Engine.HP)
# Fixing Nissan Leaf HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Nissan"&is.na(CarData$Engine.HP),177,CarData$Engine.HP)
# Fixing Tesla Model S HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Tesla"&is.na(CarData$Engine.HP),503,CarData$Engine.HP)
# Fixing Mercedes-Benz M-Class S HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Mercedes-Benz"&is.na(CarData$Engine.HP),350,CarData$Engine.HP) 
# Fixing Toyota RAV4 HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Toyota"&is.na(CarData$Engine.HP),203,CarData$Engine.HP) 
# Fixing Kia Soul EV HP NA value based on research on mean Horsepower
CarData$Engine.HP = ifelse(CarData$Make=="Kia"&is.na(CarData$Engine.HP),109,CarData$Engine.HP)

@@

@@

# Look at summary of data
summary(CarData$VehicleStyle)
# Look at missing Data if any
# missingData = CarData[rowSums(is.na(CarData)) > 0,]
# missingData
# dim(missingData)
write.csv(CarData,"CleanedCarData.csv",row.names = FALSE)
